---
title: "Bootstrapped Confidence Interval for Proportions"
author: "Joe Walderman"
date: "3/5/2021"
output: 
  html_document:
    theme: lumen
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(here)
library(boot)
library(gt)
library(broom)
```

## Bootstrapped Analsis of Exclusion, Hostility, and Intimidation Experience at UCSB

```{r}
# Make vector of community member responses, 1 being yes and 0 being no
survey <- c(0,0,0,0,0,0,0,0,0,0,0,0,0,0,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1,1)

# Function for proportion calculation by summing all responses and dividing by total quantity 
proportion <- function(x,i){sum(x[i])/36}

# Bootstrap 100,000 samples
boot_100k <- boot(survey,
                  statistic = proportion,
                  R = 100000)

boot_tidy <- tidy(boot_100k)

# Make a data frame
survey_df <- data.frame(proport = boot_100k$t)

# Plot it
ggplot(data = survey_df, aes(x = proport)) +
  geom_histogram() +
  theme_minimal() +
  labs(x = "Proportion", 
       y = "Count")
  
```

```{r}
# Confidence internval
ci <- boot.ci(boot_100k, conf = 0.95)

# Find the bootstrapped proportions mean
boot_mean <- boot_tidy %>% 
  mutate(mean = mean(boot_100k$t))
```

Bootstrapping analysis using 100,000 bootstrapped samples suggest that an average of `r round(boot_mean[4]*100,2)`% nonbinar/genderqueer students answered that they had experienced "exclusionary, offensive, hostile, or intimidating conduct", with a confidence interval of [0.44, 0.78]. The analysis had a bias of `r format(as.character(round(boot_mean[2],4)))` and a standard error of `r round(boot_mean[3],3)`.

```{r}
boot_mean %>% 
  gt() %>% 
  fmt_number(
    columns = vars(bias),
    decimals = 4
  ) %>% 
  fmt_number(
    columns = vars(std.error),
    decimals = 3
  ) %>% 
  fmt_percent(
    columns = vars(statistic, mean),
    decimals = 2
  ) %>% 
  tab_header(
    title = "Results of Bootstrap Analysis"
  ) %>% 
  cols_label(
    statistic = "Statistic",
    std.error = "Standard Error",
    mean = "Bootstrap Mean",
    bias = "Bias"
  ) %>% 
  tab_options(
    table.width = pct(50)
  )

ci
```

## Citation:
[Rankin & Associates Consulting. "UCSB Campus Climate Project Final Report." 2014.](https://campusclimate.ucop.edu/_common/files/pdf-climate/ucsb-full-report.pdf)




